A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-01 mt-marathon.2013/PBML_article.tex
start adding bibs

\section{Hypothesis Evaluation}
\subsection{Old Framework}
The types of feature functions were hardcoded when evaluating the scores of translation rules and hypotheses. For example, a translation rule is scored according to Equation (1)

\begin{equation}
  score = \sum_{i \in T}(\lambda_i * score_i) + \sum_{i  \in L} (\lambda_i * score_i) + \lambda_{wp} * words
\end{equation}

where $T$ is the set of translation models, and $L$ is the set of sequence models.

Similarly, when evaluating a hypothesis, the score is calculated as follows:

\begin{equation}
 score =  \sum_{i \in T} (\lambda_i * score_i)
    + \sum_{i \in L} (\lambda_i * score_i)
    + \lambda_{wp} * words
    + \lambda_d * score_d
    + \sum_{i \in R}(\lambda_i * score_i)
    + score_{future}
\end{equation}

>>>>

\section{Hypothesis and Translation Rule Evaluation}
\subsection{Old Framework}
The range of feature functions were hardcoded when evaluating the scores of hypotheses and translation rules. Translation rules are evaluated according to Equation~\ref{eq:translation rule score}
\begin{equation}
  score = \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_i) + \sum_{l  \in L} (\lambda_l * score_i) + \lambda_{wp} * words
\label{eq:translation rule score}
\end{equation}
where $T$ is the set of translation models, and $L$ is the set of sequence models, $\lambda_{m,i}$ is the i'th weight for translation model $m$, $\lambda_l$ is the weight for language model $l$, $\lambda_{wp}$ is the word penalty weight.

Similarly, hypotheses are evaluated as follows, Equation~\ref{hypothesis rule score}:
\begin{equation}
 score =  \sum_{i \in T} (\lambda_i * score_i)
    + \sum_{i \in L} (\lambda_i * score_i)
    + \lambda_{wp} * words
    + \lambda_d * score_d
    + \sum_{i \in R}(\lambda_i * score_i)
    + score_{future}
\label{hypothesis rule score}
\end{equation}
